Notes on Wide Gap

### 2016-05-09 paper/wide_gap_notes.tex
bcs fixed
various limits of widegap linear eqns

Thus our final boundary conditions are $\Psi = u = A = \partial_r \Psi = \partial_r(r B_\phi) = 0$, for a total of ten boundary conditions.

@@

>>>>

Thus our final boundary conditions are $\Psi = u = A = \partial_r \Psi = \partial_r(r B_\phi) = 0$, for a total of ten boundary condition equations.

@@

Discussion:

The MRI is a complicated three-dimensional instability
